---
title: "Fundamentals of R"
author: "Madison Sparks"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Exercise 1
```{r}
a<- sum(2000:20000)
a

```
Exercise 2

```{r, results='hold'}
a <- 5
b <- 2:20
a
b
```

This code assigned the integer value 5 to the object a and the array of integers from 2 to 20 to the object b.

Exercise 3
```{r, results='hold', error=TRUE}
d <- "I just want to be deleted"
d
ls() 
rm(d)
ls()
d #error bc removed 
```
```{r, results='hold'}
c<- a + b
cc <- sum(a,b)

c
cc

```
These are different results. sum adds the values associated with the objects, + adds the value of a to each integer in the array of b

Exercise 4
```{r, results='hold'}

sum4=sum(b[5:11])
sum4
```

Exercise 5
```{r, results='hold'}

sum5=sum(b[c(3,8,10)])
sum5
```

Exercise 6
```{r, results='hold'}
m <- matrix(data=1:25,ncol=5,byrow=T)
m
m[5,5]
```
The first number is for the row, the second number is for the column. m[3,] selects all the data in the 3rd row.




